Turbulence in compact to giant HII regions

### 2022-04-18 strucfunc_paper.tex
Half way through description of Orion results
Still need to finish description of covariances, and then of non
homogeneous large-scale behavior

\begin{figure}
  \centering
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-OrionS}
  \caption{
    Example corner plot of covariances between
    model parameters of fits to the \ha{} structure function.
    The example shown is for Orion,
    while figures for the remaining regions are given in
    Appendix~\ref{sec:addit-covar-corn}. 
  }
  \label{fig:corner-example-Orion}
\end{figure}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.

\subsection{Technical details of the model fits}
\label{sec:techn-deta-model}

@@

\subsection{Results of model fitting}
\label{sec:results-model-fitt}

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-OrionS}
  \caption{
    Example corner plot of covariances between
    model parameters of fits to the \ha{} structure function.
    The example shown is for Orion,
    while figures for the remaining regions are given in
    Appendix~\ref{sec:addit-covar-corn}.
    Plots on the diagonal show the 1-dimensional histogram
    of the posterior distribution of each parameter
    (labeled at bottom),
    as calculated by the MCMC method,
    assuming a uniform prior distribution
    within the limits given in Table~\ref{tab:parameter-ranges}.
    Off-diagonal plots show the 2-dimensional histogram of the
    joint posterior distribution each pair of parameters.
  }
  \label{fig:corner-example-Orion}
\end{figure}

@@

In order to provide a uniform description of the velocity fluctuations,
we fit the model structure function
\(\tilde{B}(r)\) of equation~\eqref{eq:sf-functional}
to each \hii{} region in our sample.
Results are shown in Figures~\ref{fig:strucfunc-fit-Galactic}, \ref{fig:strucfunc-fit-MC},
and \ref{fig:strucfunc-fit-ExtraGal}, arranged in order of increasing distance.
Best-fit values for the model parameters,
together with 95\% credibility range,
are given in Table~\ref{tab:Res}.
After describing the methods used to
measure the structure function and fit the model (section~\ref{sec:techn-deta-model}),
we give details of the results in the example case of
the inner Orion Nebula (\ref{sec:example-results-orion})
and a broad overview of the results for other regions (\ref{sec:results-model-fitt}).
Further details of the results for individual regions are
given in Appendix~\ref{sec:notes-individual-hii}.

\subsection{Technical details of structure function measurement and fitting}
\label{sec:techn-deta-model}

@@

\subsection{Example results of model fitting to the Orion Nebula}
\label{sec:example-results-orion}

This dataset is among the highest quality of those in our sample,
with more than \num{e5} spatial points and a factor of more than \num{500}
between the smallest and largest separations.
As a result, the observationally derived structure function (Figure~\ref{fig:strucfunc-fit-Galactic}a)
is very smooth and the model fit is very well constrained,
as evidenced by the tight credibility limits on the model parameters.
The derived correlation length \(r_0 = \SI{0.068}{pc}\) is \num{7} times smaller
than the box size, which indicates that there should be a moderate finite map effect
(section \ref{sec:effects-observ-limit-large} and Appendix~\ref{sec:finite-box-effects}),
but it is well within the range where the model fit can give reliable measurements
(see Figure~\ref{fig:finite-box-effect}).
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\) is more than \num{30} times smaller
than \(r_0\), meaning that the seeing has a negligible effect at the correlation scale and above.

Figure~\ref{fig:corner-example-Orion} shows the covariances
between parameters in the model fit.

\subsection{Results of model fitting to other sources}
\label{sec:results-model-fitt}

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.

This suggest that two episodes of star formation, at least, have taken place in the GEHR.
